Computational biology in the 21st century:\\Scaling with compressive algorithms

### 2015-09-19 main.tex
Subtitle change per Bonnie's suggestion
Minor changes to types of biological data

\title{Computational biology in the 21st century:\\The growth of compressive 
omics}
\numberofauthors{3}

@@

\section{Types and sources of biological data}

@@

\emph{Sequence} data, either 
nucleotide sequences (using a four-letter alphabet representing the four
DNA or RNA bases) or protein sequences (using a twenty-letter alphabet 
representing the twenty standard amino acids)
are obtained in several ways.
For protein and RNA sequence data, mass spectrometry---which
can determine protein sequence, as well as interactions---and RNA-seq---which can determine RNA sequence and abundance, 
allowing scientists to also infer the expression of the gene to which it might translate---play central roles.
However, with the advent of next-generation sequencing (NGS) technologies, the greatest volume of sequence data available are that of DNA.
To better understand the structure of NGS sequence data, we expand a little on NGS methodologies.

>>>>

\title{Computational biology in the 21st century:\\Scaling with compressive algorithms}
\numberofauthors{3}

@@

\section{Types of biological data}

@@

Sequence data, either 
nucleotide sequences (using a four-letter alphabet representing the four
DNA or RNA bases) or protein sequences (using a twenty-letter alphabet 
representing the twenty standard amino acids)
are obtained in several ways.
For protein and RNA sequence data, mass spectrometry---which
can determine protein sequence, as well as interactions---and RNA-seq---which can determine RNA sequence and abundance, 
allowing scientists to also infer the expression of the gene to which it might translate---play central roles.
However, with the advent of next-generation sequencing (NGS) technologies, the greatest volume of sequence data available are that of DNA.
To better understand the structure of NGS sequence data, we expand a little on NGS methodologies.
